Double White Dwarf Mergers on Adaptive Meshes\\ I. Methodology and Code Verification

### 2015-08-08 papers/wdmerger_I/paper.tex
Add GitHub links for BoxLib and Castro.

To study the white dwarf merger problem, we use the grid-based
hydrodynamics code CASTRO \citep{castro}. CASTRO solves the Euler
equations, along with the inclusion of optional modules for gravity,
nuclear reactions and thermodynamics. CASTRO is based on the BoxLib
adaptive-mesh refinement (AMR) framework \citep{rendleman:2000}, which
represents fluid data on a mesh where regions of interest have higher
spatial resolution. CASTRO is highly parallel and is designed for
large-scale use on modern supercomputers; see 
\autoref{sec:Performance} for information on how CASTRO performs for our
problem. The next few subsections describe our approach to each of the
physics components used in this work. We direct the reader to the
original code paper for a full description of CASTRO's approach to
solving the equations of hydrodynamics. In this work, we report mainly
on the changes we have made to the code since its original release,
for the purpose of approaching this problem.

@@

The software used to generate the test problems in this paper
(as well as the manuscript itself),
\texttt{wdmerger}\footnote{\url{https://github.com/BoxLib-Codes/wdmerger}},
is freely available at an online repository hosting service.
Version control in both the parent software (BoxLib, CASTRO) and in \texttt{wdmerger}
permits us to reference the state of the code at the time a simulation
was performed. In all plot files and diagnostic output generated by CASTRO, 
and EPS figure files and plots generated by \texttt{wdmerger} for this work,
we store the active \texttt{git} commit hashes of BoxLib, CASTRO and \texttt{wdmerger}.
Line plots are generated using the \texttt{matplotlib} library for \texttt{Python} 
\citep{matplotlib}, while slice plots and other multi-dimensional visualizations are 
generated using the \texttt{yt} code \citep{yt}.

>>>>

To study the white dwarf merger problem, we use the grid-based
hydrodynamics code CASTRO\footnote{CASTRO can be obtained at \url{https://github.com/BoxLib-Codes/Castro}.} \citep{castro}.
CASTRO solves the Euler
equations, along with the inclusion of optional modules for gravity,
nuclear reactions and thermodynamics. CASTRO is based on the BoxLib
\footnote{BoxLib can be obtained at \url{https://github.com/BoxLib-Codes/BoxLib}.}
adaptive-mesh refinement (AMR) framework \citep{rendleman:2000}, which
represents fluid data on a mesh where regions of interest have higher
spatial resolution. CASTRO is highly parallel and is designed for
large-scale use on modern supercomputers; see 
\autoref{sec:Performance} for information on how CASTRO performs for our
problem. The next few subsections describe our approach to each of the
physics components used in this work. We direct the reader to the
original code paper for a full description of CASTRO's approach to
solving the equations of hydrodynamics. In this work, we report mainly
on the changes we have made to the code since its original release,
for the purpose of approaching this problem.

@@

The software used to generate the test problems in this paper
(as well as the manuscript itself),
\texttt{wdmerger}\footnote{\texttt{wdmerger} can be obtained at \url{https://github.com/BoxLib-Codes/wdmerger}.},
is freely available at an online repository hosting service.
Version control in both the parent software (BoxLib, CASTRO) and in \texttt{wdmerger}
permits us to reference the state of the code at the time a simulation
was performed. In all plot files and diagnostic output generated by CASTRO, 
and EPS figure files and plots generated by \texttt{wdmerger} for this work,
we store the active \texttt{git} commit hashes of BoxLib, CASTRO and \texttt{wdmerger}.
Line plots are generated using the \texttt{matplotlib} library for \texttt{Python} 
\citep{matplotlib}, while slice plots and other multi-dimensional visualizations are 
generated using the \texttt{yt} code \citep{yt}.
